Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-15 paper/ms.tex

We analyzed the ``short'' 120-second cadence data acquired by TESS
between July~2018 and Sep~2022 (Sectors 1-55).  Specifically, we used
the 120-second cadence light curves produced by the Science Processing
and Operations Center at NASA Ames \citep{2016SPIE.9913E..3EJ}.  While
the TESS data products from these sectors also included full frame
images with cadences of 600 and 1800 seconds, we limited our scope in
this study for the sake of simplicity in data handling.  In exchange,
we sacrificed both completeness and homogeneity of the selection
function.  While TESS cumulatively observed $\approx$90\% of the sky
for at least one lunar month between July~2018 and Sep~2022, the
120-second cadence data were collected for only a subset of observable
stars during this time due to telemetric constraints
\citep[see][]{2021PASP..133i5002F}.

To assess the completeness of the resulting 120-second cadence data
that is the basis of this study, we cross-matched TIC8
\citep{2018AJ....156..102S} against the Gaia DR2 point-source catalog
\citep{2018A&A...616A...1G}.  We opted for Gaia DR2 rather than DR3
because the base catalog for TIC8 was Gaia DR2, which facilitated a
one-to-one crossmatch using the Gaia source identifiers.  This
exercise showed that for $T$$<$16 M dwarfs, the TESS 2-minute data are
$\approx$50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
of the $T$$<$16 M dwarfs have at least one sector of short-cadence
data; at $>$100\,pc, $\lesssim$10\% of such M dwarfs have at least one
sector of short-cadence data.  Armed with this understanding, we then
used our cross-match between Gaia DR2 and TIC8 to select our stars of
interest, which we defined as stars with 120-second cadence TESS light
curves that satisfied
\begin{align}
  T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only}) \\
  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})  \\
  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}),
\end{align}
for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
arcseconds, and a geometric distance $d$ defined by inverting the
parallax and ignoring any zero-point correction.  The target sample
therefore includes \nstarssearched\ M dwarfs and late-K dwarfs, down
to $T$$<$16 and out to $d$$<$150\,pc.

@@

For our dip-counting pipeline, we began with the PDC\_SAP flux for
each sector, removed non-zero quality flags, and normalized the light
curve to one by dividing out its median value.  We then flattened the
light curve using a 5-day sliding median filter, as implemented in
\texttt{wotan} \citep{2019AJ....158..143H}.  On the resulting cleaned
and flattened light curve, we ran a periodogram search, opting for the
\citet{1978ApJ...224..953S} phase dispersion minimization (PDM)
algorithm implemented in \texttt{astrobase}
\citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
below 2 days was identified, we reran the periodogram at a finer grid
to improve the accuracy of the period determination.

Once a star's period $P$ was identified, we binned the phased light
curve to 100 points per cycle.  To separate ``sharp'' local minima
from smooth spot-induced variability, we then iteratively fit robust
penalized splines to the wrapped phase-folded light curve, excluding
points more than two standard deviations away from the local continuum
\citep{2019AJ....158..143H}.  The maximum number of equidistant spline
knots per cycle is the parameter in this framework that controlled the
meaning of ``sharp'' --- we allowed at most 10 such knots per cycle,
though for most stars fewer knots were preferred based on
cross-validation using an $\ell^2$-norm penalty.  An example fit is
shown in panel {\it (e)} of Figure~\ref{fig:vet}.

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f2.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Validation plots used to  label CQVs}.  The complete figure
			set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable}
			is available online {\bf For internal collaboration review:
				\url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
			Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
      The adopted period is given in the lower-right corner.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
			{\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
			circles displayed for scale.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the automated spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
			The gray background denotes stars within 100\,pc.
			{\it l)}: Information from Gaia DR2, TIC8, and the automated
			dip-counting search pipeline.  ``Neighbors'', abbreviated
			``nbhr'', are listed within apparent distances of 2 TESS pixels
			if $\Delta T$$<$2.5.
			{\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
			using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

@@

For a few cases where BANYAN\,$\Sigma$ yielded ambiguous results, we
consulted the meta-catalog of young, age-dated, and age-dateable stars
within a kiloparsec from \citet{2022AJ....163..121B}, and also
searched the local volume around each star for co-moving
companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
commit \texttt{278b372}}

@@

Of our \ncqvsnodebunked\ confirmed and candidate CQVs, \nnotfieldbanyan\
were associated with a nearby moving group or open cluster, primarily using
BANYAN\,$\Sigma$.\footnote{Two of the
	\nnotfieldbanyan\ memberships were made with low confidence and are flagged
	in Table~\ref{tab:thetable}.
	One membership, of TIC~397791443 in IC\,2602, was made manually
	from a literature search
	\citep[e.g.][]{2020A&A...633A..99C}.}  
The relevant groups are listed in
Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  
The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
were also identified in the Argus association
\citep{2019ApJ...870...27Z}, which serves as an indirect line of
evidence supporting the reality and youth of that group.  The yield
in Sco-Cen is not surprising, since Sco-Cen contains the majority of
pre-main-sequence stars in the solar neighborhood, any many of its stars
were selected for TESS 120-second cadence observations by various
guest investigators.  Given the
$\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there may
be many more CQVs in Sco-Cen that remain to be discovered.

@@

Our search confirms that the CQV phenomenon persists for at least
$\approx$150\,Myr.  Table~\ref{tab:thetable} includes three
$\approx$150\,Myr CQVs in AB~Dor \citep{2015MNRAS.454..593B}, a
$\approx$112\,Myr old Pleiades CQV \citep{2015ApJ...813..108D}, and a
similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
knowledge, TIC~332517282 in AB~Dor was the previous record-holder for
oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
least one unambiguous CQV (EPIC~211070495) and a few other candidates
were also previously known in the Pleiades
\citep{2016AJ....152..114R}.

@@

Most CQVs in our catalog did not show infrared excesses in the W1-W4
bands, which is typical for this class of object
\citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
\nallcands\ star sample and the WISE images available through IRSA, we
labeled two objects as having reliable infrared excesses (both W3 and
W4 at $>$3$\sigma$ above the photospheric prediction).

The two IR excess sources were TIC~193136669 (TWA~34) and TIC~57830249
(TWA~33).  Both are in the TW Hydrae association ($\approx$10\,Myr),
and have relatively long periods of 38\,hr and 44\,hr respectively.
In our initial labeling, we labeled both as ``ambiguous'' CQVs because
the dips in their light curves did not show the rigid periodicity
typical of CQVs;  their periods were also relatively long.  However,
inspection of further sectors clarified that both sources are dippers
(see online plots in Figure~\ref{fig:vet}).  Independently, TIC
193136669 has a cold molecular disk based on observed 1.3\,mm
continuum emission and resolved Keplerian $^{12}{\rm CO}(2-1)$
emission \citep{2015A&A...582L...5R}.  It was also labeled a dipper by
\citet{2022ApJS..263...14C}; we agree with their designation, and
label it an ``impostor'' CQV in Table~\ref{tab:thetable}.  TIC
57830249 (TWA~33) also has previously detected 1.3\,mm continuum
emission \citep{2015A&A...582L...5R}, suggestive of cold dust grains
being present.  It is also a dipper.  Section~\ref{subsec:discdippers}
highlights plausible evolutionary connections between CQVs and dippers
in light of these ``misclassifications'' .

@@

{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of color.\footnote{For
an explanation of the renormalized unit weight error (RUWE), see the
GAIA DPAC technical note \url{http://www.rssd.esa.int/doc_fetch.php?
id=3757412}.}  Elevated RUWEs imply excess noise relative to a
single-source astrometric model.  This can be caused by marginally
resolved point sources skewing the single-transit centroid
measurements,  intrinsic photometric variability, or intrinsic
astrometric motion.  Based on this exercise, we adopted a threshold of
RUWE$_{\rm DR3}$ $>$ 2 to flag sources with excess astrometric noise.
This threshold was met for \ngoodhighruwe/\ngoods\ high-quality CQVs;
\nmaybehighruwe/\nmaybes\ of the ambiguous sample
had this characteristic.
There is some subjectivity in where to set the threshold, since the RUWE distribution has
an extended tail \citep[e.g.][]{2022MNRAS.513.5270P}.
If we had instead required RUWE$_{\rm DR3}$ $>$ 1.4,
\ngoodweakruwe/\ngoods\ high-quality CQVs and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample
would have been flagged.

{\it Gaia DR3 non-single stars}---Gaia DR3 included a
``non\_single\_star'' column that flagged known or suspected
eclipsing, astrometric, and spectroscopic binaries.  None of the stars
in our CQV sample were identified as possible binaries in this column.

@@

A small fraction of our objects were in regions of sky with
many sectors of adjacent TESS data.  Out of this already small sample, LP 12-502
(TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood out due to the
quality and content of its data.  We discuss another interesting
source, TIC~300651846, in Appendix~\ref{app:tic3006}.  In this
section, we first present the LP 12-502 observations
(Section~\ref{subsec:lpobservations}), and then highlight their
implications (Section~\ref{subsec:lplessons}).

@@

The closest CQV in our catalog is DG~CVn (TIC~368129164;
$d$$=$18\,pc), a member of AB Dor.  To our knowledge, this manuscript
is the first time that it has been noted as a CQV.  The three
brightest CQVs are DG~CVn ($T$=9.3), TIC~405754448 ($T$=9.6), and
TIC~167664935 ($T$=10.3).  The shortest period belongs to
TIC~201789285, at 3.64\,hr.  The longest period belongs to
TIC~405910546, at 37.9\,hr.  If the latter source turns out to be an
eclipsing binary, the next-longest would be TIC~193831684 (31.0\,hr).

@@

A periodic signal repeats exactly; the CQVs do not
(Figure~\ref{fig:evoln}).  While their periods appear to remain
constant to within measurement precision over thousands of cycles, the
light curve shapes evolve over 10 to 1{,}000 cycles.  They are
therefore {\it quasi}periodic.  This observation is consistent studies
by \citet{2022AJ....163..144G} and \citet{2023ApJ...945..114P}.
However it marks a qualitative departure from the ``persistent'' {\it
vs.} ``transient'' flux dip distinction described by
\citet{2017AJ....153..152S};  since all CQV dips seem to be transient
over timescales of more than 1{,}000 cycles (Figure~\ref{fig:evoln}).

With that said, one might expect a truly quasiperiodic process to be
able to explore all phase angles with equal weight.  LP 12-502, and
perhaps other CQVs, seem to have preferred phases.  For LP 12-502, all
of the dips happen over phases corresponding to only two thirds of the
period (Figure~\ref{fig:lp}).  The remaining third seems to be ``out
of limits'' for any dipping material.  This could be evidence that
the stellar magnetic field is strongly asymmetric, such that it can
hold extrinsic material at corotation, but only over two
thirds of the equatorial circle.  Alternatively, the source of the
material (e.g. a planetesimal swarm) might be distributed over an arc
of the same angular extent (240$^\circ$).  We favor the former
explanation, for reasons discussed below.

@@

CQVs show broadband flux variations that can be 1-2$\times$ deeper in
the blue than in the red
\citep{2017PASJ...69L...2O,2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
For neutral hydrogen to produce this effect in absorption, its opacity
must be larger in the blue than in the red.
\citet{1992oasp.book.....G} suggests that this might be
microphysically possible: while bound-bound absorption provides
opacity only at narrow resonant lines, the hydrogen opacity due to
bound-free absorption is ``jagged'' \citep[see][Figure 8.5 and
Eq.~8.8]{1992oasp.book.....G}, such that at temperatures of
$\approx$3{,}000\,K to $\approx$10{,}000\,K the observed chromaticities
might be reproduced.  While bound-free absorption of
${\rm H}^{-}$ seems like it should be important at such cool temperatures, in
detail this opacity source has the {\it opposite sign} from
what is required to produce deeper dips in the blue than in the red.
Thompson scattering is similarly ruled out, because it is gray.
The final plausible alternative opacity
source is dust, which has the requisite larger absorption
cross-section in the blue than the red \citep{1989ApJ...345..245C}.

@@

Independent of the microphysical basis for gas absorption, the
observed lifetime of the CQV phenomenon could provide another
dimension to discern between the gas {\it vs.} dust clump scenarios.
Based on the available statistics from e.g.
\citet{2022AJ....164...80R} and references therein, it seems plausible
that CQV occurrence decreases in time, bottoming to zero well before
the $\approx$700\,Myr age of Praesepe.  This is odd in the context of
the prominence scenario, because pre-main-sequence M dwarfs spin up
over the first $\approx$$10^8$\,yr; prominences might even be expected
to be {\it more} common at the age of the Pleiades than for younger
stars.  This broadly assumes that any star that can support
prominences will, and that the magnetic topology of rapidly rotating M
dwarfs at 100\,Myr is similar to that of rapidly rotating M dwarfs at
say, 10\,Myr.  Based on the degree to which M dwarfs remain rapid
rotators over the first few gigayears of their lives
\citep[e.g.][]{2022AJ....164...80R,2022ApJ...936..109P}, it seems
surprising in the gas clump (prominence) scenario that very few stars
older than 150\,Myr have been seen to exhibit the phenomenon.  In the
dust clump scenario this is not a problem, because if the dust were
externally sourced, it would be expected to have a finite supply.

@@

In identifying the two candidate CQVs with outlying SEDs
(TICs~193136669 and TIC~57830249; Section~\ref{subsec:irexcess}), we
were prompted to reconsider our light curve-based labeling, and
ultimately concluded that these sources are dippers.  This episode
suggests that there could be overlap between CQVs and dippers.  It is
also worth emphasizing that our labeling of e.g.~TIC~57830249 was
based on a single sector of TESS data (Sector~36) when its behavior was
relatively periodic and it showed dip depths of a few percent.
However in other TESS sectors (e.g. Sector~10), this source looks
completely different, varying in apparent flux by a factor of two,
with no discernible periodicity at all.

@@

An argument against the connection between CQVs and the $\sigma$~Ori~E
analogs is that the light curve of $\sigma$~Ori~E is much simpler than
those in Figure~\ref{fig:cqvs}, with only two broad local minima, and
one ``hump'' (Figure~\ref{fig:bstar}; see also
\citealt{2022ApJ...924L..10J}).  Within the model proposed by Townsend
et al., this is explained by the simplicity of the star's magnetic
field, which is well-approximated by a dipole, similar to most other
magnetic B stars \citep{2007A&A...475.1053A,2009ARA&A..47..333D}.
The magnetic axis needs to be tilted relative to the stellar spin
axis in order to match the qualitative behavior of both the
broadband light curves, and the line-profile variations seen in
hydrogen, helium, and carbon \citep{2012MNRAS.419..959O}.

@@

In this work, we searched 120-second cadence TESS data collected
between July~2018 and Sep~2022 for complex quasiperiodic variables
(CQVs).  The target stars were \nstarssearched\ K and M dwarfs within
150\,pc.  The selection function was $>$$80\%$ complete within 30\,pc,
and $<$$10\%$ complete at distances exceeding 100\,pc.

>>>>

To construct our sample, we analyzed the short-cadence data acquired by TESS
between 2018 July 25 and 2022 September 1 (Sectors 1-55).  Specifically, we used
the 120-second cadence light curves produced by the Science Processing
and Operations Center at NASA Ames \citep{2016SPIE.9913E..3EJ}.  While
the TESS data products from these sectors also included full frame
images with cadences of 600 and 1800 seconds, we limited our scope in
this study for the sake of simplicity in data handling and some degree of 
uniformity in the properties of the data itself.  In exchange,
we sacrificed both completeness and homogeneity of the selection
function.  While TESS cumulatively observed $\approx$90\% of the sky
for at least one lunar month between 2018 July and 2022 September, the
120-second cadence data were collected for only a subset of observable
stars during this time due to telemetric constraints
\citep[see][]{2021PASP..133i5002F}.

To assess the completeness of the resulting 120-second cadence data
that is the basis of this study, we cross-matched TIC8
\citep{2018AJ....156..102S} against the Gaia DR2 point-source catalog
\citep{2018A&A...616A...1G}.  We opted for Gaia DR2 rather than DR3
because the base catalog for TIC8 was Gaia DR2, which facilitated a
one-to-one crossmatch using the Gaia source identifiers.  This
exercise showed that for $T$$<$16 M dwarfs, the TESS 2-minute data are
$\approx$50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
of the $T$$<$16 M dwarfs have at least one sector of short-cadence
data; at $>$100\,pc, $\lesssim$10\% of such M dwarfs have at least one
sector of short-cadence data.  Armed with this understanding, we then
used our cross-match between Gaia DR2 and TIC8 to select our stars of
interest, which we defined as stars with 120-second cadence TESS light
curves satisfying these four conditions:
\begin{align}
  T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only})\\
  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})\\
  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}).
\end{align}
Here, $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ is the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ is the parallax in units of
arcseconds, and $d$ is a geometric distance defined by inverting the
parallax and ignoring any zero-point correction.  The target sample
therefore includes \nstarssearched\ M dwarfs and late-K dwarfs, down
to $T$$<$16 and out to $d$$<$150\,pc.

@@

For our dip-counting pipeline, we began with the {\tt PDC\_SAP} flux for
each sector, removed non-zero quality flags, and normalized the light
curve to one by dividing out its median value.  We then flattened the
light curve using a 5-day sliding median filter, as implemented in
\texttt{wotan} \citep{2019AJ....158..143H}.  On the resulting cleaned
and flattened light curve, we ran a periodogram search, opting for the
\citet{1978ApJ...224..953S} phase dispersion minimization (PDM)
algorithm implemented in \texttt{astrobase}
\citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
$P$ below 2 days was identified, we reran the periodogram at a finer grid
to improve the accuracy of the period determination.

Once a star's period was identified, we binned the phased light
curve to 100 points per cycle.  To separate ``sharp'' local minima
from smooth but double-dipped spot variability, we then iteratively
fit robust penalized splines to the wrapped phase-folded light curve,
excluding points more than two standard deviations away from the local
continuum \citep{2019AJ....158..143H}.  The maximum number of
equidistant spline knots per cycle is the parameter in this framework
that controlled the meaning of ``sharp'' --- we allowed at most 10
such knots per cycle, though for most stars fewer knots were preferred
based on cross-validation using an $\ell^2$-norm penalty.  An example
fit is shown in panel {\it (e)} of Figure~\ref{fig:vet}.

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f2.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Validation plots used to  label CQVs}.  The complete figure
			set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable}
			is available in the online journal. {\bf For internal collaboration review:
				\url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
			Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
      The adopted period is given in the lower-right corner.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
			{\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
			circles displayed for scale.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the automated spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
			The gray background denotes stars within 100\,pc.
			{\it l)}: Information from Gaia DR2, TIC8, and the automated
			dip-counting search pipeline.  ``Neighbors'', abbreviated
			``nbhr'', are listed within apparent distances of 2 TESS pixels
			if $\Delta T$$<$2.5.
			{\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
			using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

@@

For a few cases where BANYAN\,$\Sigma$ yielded ambiguous results, we
consulted the meta-catalog of young, age-dated, and age-dateable stars
within from \citet{2022AJ....163..121B}, and also
searched the local volume around each star for co-moving
companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
commit \texttt{278b372}}

@@

Of our \ncqvsnodebunked\ confirmed and candidate CQVs, \nnotfieldbanyan\
were associated with a nearby moving group or open cluster, primarily using
BANYAN\,$\Sigma$.\footnote{Two of the
	\nnotfieldbanyan\ memberships were made with low confidence and are flagged
	in Table~\ref{tab:thetable}.
	One membership, of TIC~397791443 in IC\,2602, was made manually
	from a literature search
	\citep[e.g.][]{2020A&A...633A..99C}.}  
The relevant groups are listed in
Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  
The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
were also identified in the Argus association
\citep{2019ApJ...870...27Z}, which serves as an indirect line of
evidence supporting the reality and youth of that group.  The yield
in Sco-Cen is not surprising since Sco-Cen contains the majority of
pre-main-sequence stars in the solar neighborhood, and many of its stars
were selected for TESS 120-second cadence observations by various
guest investigators.  Given the
$\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there may
be many more CQVs in Sco-Cen that remain to be discovered.

@@

Our search confirms that the CQV phenomenon persists for at least
$\approx$150\,Myr.  Table~\ref{tab:thetable} includes three
$\approx$150\,Myr CQVs in AB~Dor \citep{2015MNRAS.454..593B}, a
$\approx$112\,Myr old Pleiades CQV \citep{2015ApJ...813..108D}, and a
similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
knowledge, TIC~332517282 in AB~Dor was the previous record-holder for the
oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
least one unambiguous CQV (EPIC~211070495) and a few other candidates
were also previously known in the Pleiades
\citep{2016AJ....152..114R}.

@@

Most CQVs in our catalog did not show infrared excesses in the $W1$-$W4$
bands, which is typical for this class of object
\citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
\nallcands\ star sample and the WISE images available through IRSA, we
labeled two objects as having reliable infrared excesses (both $W3$ and
$W4$ at $>$3$\sigma$ above the photospheric prediction).

The two sources exhibiting an IR excess were TIC~193136669 (TWA~34) and TIC~57830249
(TWA~33).  Both are in the TW Hydrae association ($\approx$10\,Myr),
and have relatively long periods of 38\,hr and 44\,hr respectively.
In our initial labeling, we labeled both as ``ambiguous'' CQVs because
the dips in their light curves did not show the rigid periodicity
typical of CQVs;  their periods were also relatively long.  However,
inspection of further sectors clarified that both sources are dippers
(see online plots in Figure~\ref{fig:vet}).  Independently, TIC
193136669 has a cold molecular disk based on observed 1.3\,mm
continuum emission and resolved Keplerian $^{12}{\rm CO}(2-1)$
emission \citep{2015A&A...582L...5R}.  It was also labeled a dipper by
\citet{2022ApJS..263...14C}; we agree with their designation, and
label it an ``impostor'' CQV in Table~\ref{tab:thetable}.  TIC
57830249 (TWA~33) also has previously detected 1.3\,mm continuum
emission \citep{2015A&A...582L...5R}, suggestive of cold dust grains
being present.  It is also a dipper.  Section~\ref{subsec:discdippers}
highlights plausible evolutionary connections between CQVs and dippers
in light of these ``misclassifications'' .

@@

{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of color.\footnote{For
an explanation of the renormalized unit weight error (RUWE), see the
GAIA DPAC technical note \url{http://www.rssd.esa.int/doc_fetch.php?
id=3757412}.}  Elevated RUWEs imply excess noise relative to a
single-source astrometric model.  This can be caused by marginally
resolved point sources skewing the single-transit centroid
measurements,  intrinsic photometric variability, or intrinsic
astrometric motion.  Based on this exercise, we adopted a threshold of
RUWE$_{\rm DR3}$ $>$ 2 to flag sources with excess astrometric noise.
This threshold was met for \ngoodhighruwe/\ngoods\ high-quality CQVs;
\nmaybehighruwe/\nmaybes\ of the ambiguous ones had this
characteristic.  There is some subjectivity in where to set the
threshold, since the RUWE distribution has an extended tail
\citep[e.g.][]{2022MNRAS.513.5270P}.  If we had instead required
RUWE$_{\rm DR3}$ $>$ 1.4, \ngoodweakruwe/\ngoods\ high-quality CQVs
and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample would have been
flagged.

{\it Gaia DR3 non-single stars}---Gaia DR3 included a
{\tt non\_single\_star} column that flagged known or suspected
eclipsing, astrometric, and spectroscopic binaries.  None of the stars
in our CQV sample were identified as possible binaries in this column.

@@

A small fraction of our objects were in regions of sky with many
sectors of adjacent TESS data.  Out of this already small sample, LP
12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood out due to
the quality and content of its data.  We discuss another interesting
source, TIC~300651846, in Appendix~\ref{app:tic3006}.  In this
section, we first present the LP 12-502 observations and then
highlight their implications.

@@

The closest CQV in our catalog is DG~CVn (TIC~368129164;
$d$$=$18\,pc), a member of AB Dor.  To our knowledge, this work
is the first time that it has been noted as a CQV.  The three
brightest CQVs are DG~CVn ($T$=9.3), TIC~405754448 ($T$=9.6), and
TIC~167664935 ($T$=10.3).  The shortest period belongs to
TIC~201789285, at 3.64\,hr.  The longest period belongs to
TIC~405910546, at 37.9\,hr.  If the latter source turns out to be an
eclipsing binary, the next-longest would be TIC~193831684 (31.0\,hr).

@@

A periodic signal repeats exactly; the CQVs do not
(Figure~\ref{fig:evoln}).  While their periods appear to remain
constant to within measurement precision over thousands of cycles, the
light curve shapes evolve over 10 to 1{,}000 cycles.  They are
therefore {\it quasi}periodic.  While this observation is consistent
with the analyses by \citet{2022AJ....163..144G} and
\citet{2023ApJ...945..114P}, it marks a qualitative departure from the
``persistent'' {\it vs.} ``transient'' flux dip distinction described
by \citet{2017AJ....153..152S}, since all CQV dips seem to be
transient over timescales of more than 1{,}000 cycles
(Figure~\ref{fig:evoln}).

With that said, one might expect a truly quasiperiodic process to be
able to explore all phase angles with equal weight.  LP 12-502, and
perhaps other CQVs, seem to have preferred phases.  For LP 12-502, all
of the dips happen over phases corresponding to only two thirds of the
period (Figure~\ref{fig:lp}).  The remaining third seems to be ``out
of limits'' for any dipping material.  This could be evidence that the
stellar magnetic field is strongly asymmetric, and can hold extrinsic
material at corotation, but only over two thirds of the equatorial
circle.  Alternatively, the source of the material (e.g. a
planetesimal swarm) might be distributed over an arc of the same
angular extent (240$^\circ$).  We favor the former explanation, for
reasons discussed below.

@@

CQVs show broadband flux variations that can be 1-2$\times$ deeper in
the blue than in the red
\citep{2017PASJ...69L...2O,2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
For neutral hydrogen to produce this effect in absorption, its opacity
must be larger in the blue than in the red.
\citet{1992oasp.book.....G} suggests that this might be
microphysically possible: while bound-bound absorption provides
opacity only at narrow resonant lines, the hydrogen opacity due to
bound-free absorption is ``jagged'' \citep[see][Figure 8.5 and
Eq.~8.8]{1992oasp.book.....G}, such that at temperatures of
$\approx$3{,}000\,K to $\approx$10{,}000\,K the observed chromaticities
might be reproduced.  While bound-free absorption of
${\rm H}^{-}$ seems like it should be important at such cool temperatures, in
detail this opacity source has the {\it opposite sign} from
what is required to produce deeper dips in the blue than in the red.
Thomson scattering is similarly ruled out as a relevant opacity
source, because it is gray.  The final plausible alternative opacity
source is dust, which has the requisite larger absorption
cross-section in the blue than the red \citep{1989ApJ...345..245C}.

@@

Independent of the microphysical basis for gas absorption, the
observed lifetime of the CQV phenomenon could provide another
dimension to discern between the gas {\it vs.} dust clump scenarios.
Based on the available statistics from e.g.
\citet{2022AJ....164...80R} and references therein, it seems plausible
that CQV occurrence decreases in time, bottoming to zero well before
the $\approx$700\,Myr age of Praesepe.  This is odd in the context of
the prominence scenario, because pre-main-sequence M dwarfs spin up
over the first $\approx$$10^8$\,yr; prominences might even be expected
to be {\it more} common at the age of the Pleiades than for younger
stars.  This broadly assumes that any star that can support
prominences will do so, and that the magnetic topology of rapidly rotating M
dwarfs at 100\,Myr is similar to that of rapidly rotating M dwarfs at
say, 10\,Myr.  Based on the degree to which M dwarfs remain rapid
rotators over the first few gigayears of their lives
\citep[e.g.][]{2022AJ....164...80R,2022ApJ...936..109P}, it seems
surprising in the gas clump (prominence) scenario that very few stars
older than 150\,Myr have been seen to exhibit the phenomenon.  In the
dust clump scenario this is not a problem, because if the dust were
externally sourced, it would be expected to have a finite supply.

@@

In identifying the two candidate CQVs with outlying SEDs
(TICs~193136669 and TIC~57830249; Section~\ref{subsec:irexcess}), we
were prompted to reconsider our light curve-based labeling, and
ultimately concluded that these sources are dippers.  This episode
suggests that there could be overlap between CQVs and dippers.  It is
also worth emphasizing that our labeling of e.g.~TIC~57830249 was
based on a single sector of TESS data (Sector~36) when its behavior was
relatively periodic and it showed dip depths of a few percent.
However, in other TESS sectors (e.g. Sector~10), this source looks
completely different, varying in apparent flux by a factor of two,
with no discernible periodicity at all.

@@

An argument against the connection between CQVs and the $\sigma$~Ori~E
analogs is that the light curve of $\sigma$~Ori~E is much simpler than
those in Figure~\ref{fig:cqvs}, with only two broad local minima, and
one ``hump'' (Figure~\ref{fig:bstar}; see also
\citealt{2022ApJ...924L..10J}).  Within the model proposed by
\citeauthor{2005ApJ...630L..81T}, this is explained by the simplicity
of the star's magnetic field, which is well-approximated by a dipole,
similar to most other magnetic B stars
\citep{2007A&A...475.1053A,2009ARA&A..47..333D}.  The magnetic axis
needs to be tilted relative to the stellar spin axis in order to match
the qualitative behavior of both the broadband light curves, and the
line-profile variations seen in hydrogen, helium, and carbon
\citep{2012MNRAS.419..959O}.

@@

In this work, we searched 120-second cadence TESS data collected
from 2018 July to 2022 September for complex quasiperiodic variables
(CQVs).  The target stars were \nstarssearched\ K and M dwarfs within
150\,pc.  The selection function was $>$$80\%$ complete within 30\,pc,
and $<$$10\%$ complete at distances exceeding 100\,pc.
